### 2010-02-15 doc/manuals/janitor/tex_maintenance/maintenance.tex
janitor.pdf builds again. Many thanks to Anders for spotting the issue.
Further update on the Janitor docs.

This chapter explains how to maintain the {\em Catalog} and the {\em Janitor}
themselves.
It gives detailed instructions how to create new packages for the
Janitor.
To administrate the catalog, it is strongly recommended
(but not ultimately required) to use the ontology editor Prot\`eg\`e,
as explained in the next section.
In the last section, a typical use case in maintaining the Janitor will
be presented.

@@

To edit the catalog, the ontology editor Prot\`eg\`e should be
used. Figure~\ref{fig:protege_example} shows the editor while the
MetaPackage \texttt{APPS/BIO/JASPAR-CORE-1.0} of the example file has
been selected.

@@

On the left side of the editor the class browser is placed. Three
main classes are prepared: \texttt{MetaPackage}, \texttt{Note} and
\texttt{Package}.

@@

MetaPackages contain one or more instances of the class
\texttt{Package}, which are then tangible software packages providing
the functionality that the MetaPackage references. The packages may
be aiming for different versions of the operating system or be different
in the way these are installed, but any package being assigned to the same
MetaPackage needs to perform the same functionality.
MetaPackages are described by the subclasses of \texttt{Note, which
in turn has two subclasses: \texttt{BaseSystem} and
\texttt{Tag}.

@@

The WEKA package for machine learning~\cite{FRANK_20074} and the Java
Runtime Environment are available as dynamic Runtime Environments. Further
packages for bioinformatics comprise dynamic variants of tools for
the analysis of transcription factor binding sites. These are already
offered for manual installation via the prior mentioned traditional page
representing Runtime Environments for ARC.  The corresponding tar file
is named \task{somewhat??}. The \texttt{data} directory simply contains
a ZIP file which needs to be unzipped in the installation directory. For
that reason, the \texttt{control/install} script is written as follows:

>>>>

This chapter explains how to maintain the {\em Catalog} and the {\em Janitor}
themselves.
It gives detailed instructions how to create new packages for the
Janitor.
To administrate the catalog, one can either use an ontology editor 
like Prot\`eg\`e, as explained in the next section, edit the documents
manually.
In the last section, a typical use case in maintaining the Janitor will
be presented.

@@

To edit the catalog, the ontology editor Prot\`eg\`e may be
used. With some experience gained, one is likely to prefer a manual editing.
Figure~\ref{fig:protege_example} shows the editor while the
MetaPackage \texttt{APPS/BIO/JASPAR-CORE-1.0} of the example file has
been selected.

@@

On the left side of the editor the class browser is placed. Three
main classes are prepared: \texttt{MetaPackage}, \texttt{Note} and
\texttt{Package}. The RDF file is kept in the RDF:XML format, and
when inspecting the entry, one will fine a direct correspondence 
to the data stored in RDF:

\begin{verbatim}
<rdfs:Class rdf:about="&kb;MetaPackage"
         rdfs:label="MetaPackage">
  <rdfs:subClassOf rdf:resource="&rdfs;Resource"/>
  <rdfs:comment>
   Reference to a piece of software that shall be made available -
   somehow, and to the expectation to the grid user.  The traditional
   way to achieve the installation is via tarballs. Debian packages may
   be an alternative.
  </rdfs:comment>
</rdfs:Class>
<rdfs:Class rdf:about="&kb;Note"
   rdfs:label="Note">
   <rdfs:subClassOf rdf:resource="&rdfs;Resource"/>
</rdfs:Class>
<rdfs:Class rdf:about="&kb;Package"
   rdfs:label="Package">
  <rdfs:subClassOf rdf:resource="&rdfs;Resource"/>
  <rdfs:comment>
   Superclass of "TarPackage" and "DebianPackage".
  </rdfs:comment>
</rdfs:Class>
\end{verbatim}

@@

Links between resources are referred to as {\em Properties}. The following
specifies the dependencies that any package may have on other resources, i.e.
on other packages. The dependency on a base system is expressed by the
property {\em basesystem}, which not to be confused with the resource
{\em BaseSystem}.

\begin{verbatim}
<rdf:Property rdf:about="&kb;depends"
         rdfs:comment="lists dependencies of this package"
         rdfs:label="depends">
        <rdfs:domain rdf:resource="&kb;Package"/>
        <rdfs:range rdf:resource="&rdfs;Resource"/>
\end{verbatim}

MetaPackages contain one or more instances of the class
\texttt{Package}, which are then tangible software packages providing
the functionality that the MetaPackage references. The packages may
be aiming for different versions of the operating system or be different
in the way these are installed, but any package being assigned to the same
MetaPackage needs to perform the same functionality.
MetaPackages are described by the subclasses of \texttt{Note}, which
in turn has two subclasses: \texttt{BaseSystem} and
\texttt{Tag}.

@@

The WEKA package for machine learning~\cite{FRANK_20074} and the Java
Runtime Environment are available as dynamic Runtime Environments. Further
packages for bioinformatics comprise dynamic variants of tools for
the analysis of transcription factor binding sites. These are already
offered for manual installation via the prior mentioned traditional page
representing Runtime Environments for ARC.
The \texttt{data} directory simply contains
a ZIP file which needs to be unzipped in the installation directory. For
that reason, the \texttt{control/install} script is written as follows:
